Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-11-23 main.tex
:pencil: Rephrase introduction

@@

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the transmission efficiency by providing a passive beamforming gain. This paper investigates an IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS. Considering the rectifier nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user. Stationary solutions are achieved based on Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by Geometric Programming (GP) technique. It is confirmed that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH), such that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR). Simulation results also show that the IRS significantly enlarges the R-E region while preserving the waveform preference and transceiving strategy. Although the AP-IRS-user extra link is relatively weak, we found that the information and power benefits of passive beamforming scale much faster than those of active beamforming. It suggests using more active antennas for small-scale SWIPT and more passive elements for large-scale SWIPT. % The proposed design enables a joint control of transmitter, receiver and wireless channel.
	\end{abstract}

@@

	\begin{section}{Introduction}
		\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks has come to energy supply. Most existing mobile devices are powered by batteries that require frequent charging or replacement, which causes high maintenance cost and restricts the scale of networks. Although solar energy and inductive coupling have become popular alternatives, the former depends on the environment while the latter has a very short operation range. Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the Radio-Frequency (RF) band. It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks. The upsurge in the number of connected devices, together with the decreasing trend in the power consumption of electronics, call for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.

			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the rectifier input power level and input waveform shape. It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then designed joint waveform and beamforming design for WPT. Simulation and experiments demonstrated that ignoring the energy harvester nonlinearity is inaccurate and emphasized the benefit of modeling such nonlinearity in real system design \cite{Kim2019,Kim2020a}. Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand the operation range. Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}. Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?". This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g. modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
		\end{subsection}

		\begin{subsection}{Intelligent Reflecting Surface}
			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the wireless channel to increase spectrum and energy efficiency. In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming. Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to Frequency-Flat (FF) reflection. Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS as active FSS requires RF-chains \cite{Kim2006} while passive FSS has fixed physical characteristics and is non-adaptive \cite{Anwar2018}.

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at a specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Wu2019}. Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting. In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each reflector with the others switched off. To reduce estimation overhead and design complexity, \cite{Yang2019} exploited the spatial correlation and proposed a group-based IRS model where adjacent elements share a common reflection coefficient. Recent research also explored the possibility of integrating IRS into Orthogonal Frequency-Division Multiplexing (OFDM) systems. For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, to enable flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

		\begin{subsection}{IRS-Aided SWIPT}
			The effective channel enhancement and low power consumption of the IRS are expected to bring more opportunities to SWIPT. It was argued in \cite{Wu2020b} that a dedicated energy beam is power-inefficient and may cause interference, thus not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system. On the other hand, \cite{Tang2019} suggested that if the interference can be canceled, multiple energy beams are generally required for the max-min harvested power problem. \cite{Wu2020a} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update the transmit precoder and the IRS phase shifts, while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated. In such cases, a single energy stream is enough for all energy receivers. However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission and consider an inaccurate and oversimplified linear energy harvester model.

			In this paper, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of the IRS. The contributions of the paper are listed as follows.

			\textit{First}, we introduce a novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design. This architecture can be seen to IRS-aided SWIPT what \cite{Clerckx2018b} is to SWIPT. Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user. A multi-carrier unmodulated power waveform (deterministic multisine) is superposed to a multi-carrier modulated information waveform to boost the energy transfer efficiency. The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS, and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity. This is the first paper to propose such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT. Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2020} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design. On the contrary, this paper focuses on multi-carrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.

			\textit{Second}, we formulate an optimization for this joint waveform, active and passive beamforming design to characterize the R-E region achieved by the proposed architecture. The R-E region characterization problem is transformed into multiple energy maximization problems subject to rate constraints. Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS, 2) waveform, active beamforming at the transmitter and power splitting ratio at the receiver, until convergence. On top of the SWIPT optimization based on Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs a low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in an efficient and reliable manner. Though no rigorous mathematical proof exists for the convergence of the relaxed IRS phase shift problem, numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.

			\textit{Third}, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture. It is confirmed that the observations for SWIPT carry on to IRS-aided SWIPT. For example, a dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, while TS and PS are preferred at low and high SNR, respectively. Results also confirmed that the IRS brings a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy. Different from the active amplify-and-forward (AF) relay with optimal location around the midpoint \cite{Li2017}, the passive IRS should be placed next to either the transmitter or the receiver due to the product-distance path loss model. It implies that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems. For active beamforming, increasing the number of transmit antennas brings a linear growth in SNR and a quadratic boost in harvested DC power. For passive beamforming, increasing the number of reflect elements provides a quadratic growth in SNR and a quartic boost in harvested DC power. Moreover, the adaptive IRS design outperforms the non-adaptive (rate/energy-optimized) ones for broadband transmission, while the performance of all three strategies coincides with the ideal Frequency-Selective (FS) IRS for narrowband transmission.

@@

		As shown in Fig.~\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands with center frequency $f_n$ ($n=1,\dots,N$). Perfect Channel State Information (CSI) at the transmitter, IRS and receiver with negligible training overhead are assumed to explore the upper bound of the proposed design. A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged. Two practical co-located receiver architectures are compared in terms of the R-E region. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and beamforming design. Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by the IRS for two and more times are omitted. We also assume the noise power is too small to be harvested.

@@

		\begin{subsection}{Composite Channel}
			At subband $n$, denote the AP-user direct channel as $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l=\alpha_l e^{j\theta_l}$ with reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. Define the IRS matrix as $\boldsymbol{\Theta} = \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries. The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel. On top of this, the total composite channel is obtained by superposing the IRS-aided auxiliary channel to the AP-user direct channel as
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{D,n}^H + \boldsymbol{h}_{R,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where $\boldsymbol{\phi}=[\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$. Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
			\begin{remark}\label{re:irs_frequency_flat}
				Due to hardware constraints, independent phase shift control for different frequencies is prohibited and the IRS is frequency-flat. Hence, the auxiliary channels at different frequencies cannot be simultaneously maximized and there is a tradeoff in subchannel alignment.
				% At subband $n$, the AP-IRS MIMO channel $\boldsymbol{H}_{I,n}$ can be divided into $L$ MISO channels between all transmit antennas and each IRS element. Reflection coefficient $\phi_l$ is shared for the $l$-th AP-IRS MISO channel of all subbands, namely $MN$ entries in total.
				The reflection coefficient of each IRS element is shared for the AP-IRS MISO channel and over all subbands, namely $MN$ entries in total.
			\end{remark}
		\end{subsection}

@@

		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$. A \textit{first} observation is that, different from the active AF relay that achieves optimal performance when developed around the midpoint, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff. It origins from the product-distance path loss model that applies to finite-size element reflection. As shown in Fig.~\ref{fi:path_loss}, although the piecewise TGn path loss model further penalizes large distance (greater than \SI{10}{\meter} for model D), it is still beneficial to have a short-long or long-short transmission setup, since signal attenuation increases fast at a short distance and experiences marginal effect at a long distance. On the other hand, it also suggests that developing an IRS next to the AP can effectively extend the operation range of SWIPT systems. Considering the passive characteristic of the IRS, opportunities are that it can be directly supported by the SWIPT network. A \textit{second} observation is that there exist two optimal IRS development locations that minimize the path loss production $\Lambda_I\Lambda_R$. It implies that more than one IRS may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the IRS.

>>>>

% reflection coefficients vs reflector vs reflection element

@@

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is severely restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the transmission efficiency by providing a passive beamforming gain. This paper investigates an effective IRS-aided SWIPT architecture where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS. Considering the energy harvester nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user. Stationary solutions are achieved based on the Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by the Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by the Geometric Programming (GP) technique. Despite the hardware limitations of IRS constraint the reflection elements to be Frequency-Flat (FF), results demonstrate the significant benefits of the proposed architecture based on a joint design of the waveform, active and passive beamforming to enlarge the R-E region of IRS-aided SWIPT.
	\end{abstract}

@@

	\begin{section}{Introduction}
		\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks has come to energy supply. Most existing mobile devices are powered by batteries that require frequent charging or replacement, which brings high maintenance cost and restricts the scale of networks. Although solar energy and inductive coupling have become popular alternatives, the former depends on the environment while the latter has a very short operation range. Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the Radio-Frequency (RF) band. It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks. The upsurge in the number of connected devices, together with the decreasing trend in the power consumption of electronics, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.

			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the input rectifier power and waveform shape. It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then designed joint waveform and beamforming design for WPT. Simulation and experiments demonstrated that ignoring the energy harvester nonlinearity is inaccurate and emphasized the benefit of modeling such nonlinearity in real system design \cite{Kim2019,Kim2020a}. Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand the operation range. Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}, which uniquely showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019}, led to the question: "what is the optimal input distribution for SWIPT under nonlinearity? ". This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g. modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
		\end{subsection}

		\begin{subsection}{Intelligent Reflecting Surface}
			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the wireless channel to increase the spectrum and energy efficiency. In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming. Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to Frequency-Flat (FF) reflection. Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS because active FSS requires RF-chains \cite{Kim2006} while passive FSS has fixed physical characteristics and is non-adaptive \cite{Anwar2018}.

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at a specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}. Moreover, \cite{Abeywickrama2019} investigated the coupling effect of reflection amplitude and phase shift based on impedance equation, and \cite{Nadeem2019} proposed a sequential cascaded channel estimation for Time-Division Duplex (TDD) systems. %To reduce the estimation overhead and design complexity, \cite{Yang2019} considered a group-based IRS model where adjacent elements share a common reflection coefficient.
			A novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems was proposed in \cite{Yang2020}, which varies the reflection coefficients over consequent slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

		\begin{subsection}{IRS-Aided SWIPT}
			The effective channel enhancement and low power consumption of the IRS are expected to bring more opportunities to SWIPT. For a multi-user IRS-aided SWIPT system, dedicated energy beams are unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when considering the fairness issue \cite{Tang2019}. It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links can boost the harvested power. In such cases, the rank-deficient channels are highly correlated such that a single energy beam can satisfy all energy receivers. However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission and consider an inaccurate and oversimplified linear energy harvester model. In this paper, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of the IRS. We ask ourselves the important question: "How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge as much as possible the R-E region of IRS-aided SWIPT? " The contributions of the paper are listed as follows.

			\textit{First}, we introduce a novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design. This architecture can be seen to IRS-aided SWIPT what \cite{Clerckx2018b} is to SWIPT. Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user. A multi-carrier unmodulated power waveform (deterministic multisine) is superposed to a multi-carrier modulated information waveform to boost the energy transfer efficiency. The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS, and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity. This is the first paper to propose such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT. Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2020} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model \cite{Clerckx2019,Clerckx2016a}), which prevents from exploiting the waveform gain in SWIPT system design. On the contrary, this paper focuses on multi-carrier IRS-SWIPT and investigates the joint design of waveform, active and passive beamforming accounting for rectenna nonlinearity.

			\textit{Second}, we formulate an optimization for this joint waveform, active and passive beamforming design to characterize the R-E region achieved by the proposed architecture. The R-E region characterization problem is transformed into multiple energy maximization problems subject to rate constraints. Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS, 2) waveform, active beamforming at the transmitter and power splitting ratio at the receiver, until convergence. On top of the SWIPT optimization by Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs a low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in an efficient and reliable manner. Numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.

			\textit{Third}, we conduct numerical evaluations to demonstrate the advantage of the proposed IRS-aided SWIPT architecture.
			% Note also that the joint waveform and beamforming design and optimization (and its potential performance benefits) in IRS-aided SWIPT differs from that in SWIPT (as in \cite{Clerckx2018b,Varasteh2019d}) due to the hardware constraint that the IRS elements should be frequency-flat.
			Despite the hardware limitations of the IRS that constraint the reflection elements to be frequency flat, numerical results show significant R-E benefits of the proposed joint waveform and beamforming design. We confirmed the main observations of SWIPT, namely a dedicated power waveform is beneficial for multi-carrier transmission, and TS/PS are preferred at low/high SNR, carry on to the IRS-aided SWIPT. Moreover, new observations are that 1) the IRS should be placed close to the transmitter or the receiver for optimal behavior, 2) the number of transmit antenna and IRS elements have no noticeable impact on the transceiving mode, 3) for active beamforming, increasing the number of transmit antennas brings a linear enhancement to the SNR and a quadratic boost to the harvested DC power, 4) for passive beamforming, increasing the number of reflect elements provides a quadratic enhancement to the SNR and a quartic boost to the harvested DC power, 5) the adaptive (i.e. rate-dependent) passive beamforming is required for broadband transmission, 6) the performance loss by the frequency-flat constraint of IRS is negligible for narrowband transmission.

			% Results also confirmed that the IRS brings a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy. Different from the active amplify-and-forward (AF) relay with optimal location around the midpoint \cite{Li2017}, the passive IRS should be placed next to either the transmitter or the receiver due to the product-distance path loss model. It implies that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems. For active beamforming, increasing the number of transmit antennas brings a linear growth in SNR and a quadratic boost in harvested DC power. For passive beamforming, increasing the number of reflect elements provides a quadratic growth in SNR and a quartic boost in harvested DC power. Moreover, the adaptive IRS design outperforms the non-adaptive (rate/energy-optimized) ones for broadband transmission, while the performance of all three strategies coincides with the ideal Frequency-Selective (FS) IRS for narrowband transmission.

@@

		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands at frequency $f_n$ ($n=1,\dots,N$). We consider a quasi-static block fading channel model and focus on one particular block where the channel responses are constant. It is assumed that the perfect Channel State Information (CSI) of all links with negligible training overhead is known at the AP. Two practical co-located receiver architectures, namely TS and PS, are compared in terms of the R-E region. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and beamforming design. Signals reflected by the IRS for two and more times are omitted, and the noise power is assumed too small to be harvested.

@@

		\begin{subsection}{Composite Channel}
			At subband $n$, denote the AP-user direct channel as $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l=\alpha_l e^{j\theta_l}$ with reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. Define the IRS matrix as $\boldsymbol{\Theta} = \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries. The auxiliary link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel. On top of this, the total composite channel is obtained by superposing the IRS-aided auxiliary channel to the AP-user direct channel as
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{D,n}^H + \boldsymbol{h}_{R,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where $\boldsymbol{\phi}=[\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$. Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
			\begin{remark}\label{re:irs_frequency_flat}
				Due to hardware constraints, independent phase shift control for different frequencies is prohibited and the IRS is frequency-flat. Hence, the auxiliary channels at different frequencies cannot be simultaneously maximized and there is a tradeoff in subchannel alignment.
				% At subband $n$, the AP-IRS MIMO channel $\boldsymbol{H}_{I,n}$ can be divided into $L$ MISO channels between all transmit antennas and each IRS element. Reflection coefficient $\phi_l$ is shared for the $l$-th AP-IRS MISO channel of all subbands, namely $MN$ entries in total.
				The reflection coefficient of each IRS element is shared for the AP-IRS MISO channel and over all subbands, namely $MN$ entries in total.
			\end{remark}
		\end{subsection}

@@

		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$. A \textit{first} observation is that, different from the active Amplify-and-Forward (AF) relay that achieves optimal performance when developed around the midpoint \cite{Li2017}, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff. It origins from the product-distance path loss model that applies to finite-size element reflection. As shown in Fig.~\ref{fi:path_loss}, although the piecewise TGn path loss model further penalizes large distance (greater than \SI{10}{\meter} for model D), it is still beneficial to have a short-long or long-short transmission setup, since signal attenuation increases fast at a short distance and experiences marginal effect at a long distance. On the other hand, it also suggests that developing an IRS next to the AP can effectively extend the operation range of SWIPT systems. Considering the passive characteristic of the IRS, opportunities are that it can be directly supported by the SWIPT network. A \textit{second} observation from Fig.~\ref{fi:path_loss} is that there exist two optimal IRS development locations that minimize the path loss production $\Lambda_I\Lambda_R$. It implies that more than one IRS may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the IRS.
